#

```{r}
library(RSelenium)
```

We need to ensure we have started the seleniumn server before we try to connecto to it.
We do this with the shell command
```{shell}
java -Dwebdriver.gecko.driver=`pwd`/geckodriver -Dwebdriver.chrome.driver=`pwd`/chromedriver -jar selenium-server-standalone-3.6.0.jar 
```
Note that the jar file (java archive) and the two executable drivers for Firefox and Chrome are in
the current directory. They don't have to be.

Back to R.
We next establish a connection to that browser instance.
```{r}
remDr = remoteDriver(browserName = 'firefox')
remDr$open()
```
We can specify a different browser, port  on which the selenium server is listening,
the IP address for a different machine on which the server is running, etc.


Now we have the browser visit the page in which we are interested using the
navigate() method.
```
u = "https://www.aepenergy.com/"
remDr$navigate(u)
```

Before we can remote control the browser to do what we want, we need
to know what it is that we want to do.
In our regular browser, let's visit this page.
We see the `CHECK SERVICE AVAILABILITY` and a `Enter ZIP`
near the top of the page. 
<img src="aepenergy1.tiff"/>

We enter a ZIP code, e.g., 45201 and then either hit the return key
or click on the ENTER link to the right of the textfield.

This changes the page to show an `ENROLL NOW` link.
<img src="aepenergy2.tiff"/>

We click on this and we get the page we actually want
with the prices for the different electricity rate deals.
<img src="aepenergy3.tiff"/>

We want to be able to do this for all of the ZIP codes in Ohio.
So we want to automate this.

<!-- change = remDr$findElement("id", "region__link--change") -->

We have already navigated the browser to the top-level URL.
Next we want to insert the ZIP code into the textfield.
To do this, we need to find the textfield element in the page.
We can use various different types of selection methods, including XPath.
We look at the HTML source for the page and identify a pattern to identify this
element.  In this case, it has a unique id attribute with a value `region__input--zip`.
So we can get a reference to this live element in the page with
the `findElement()` method of the remote driver:
```{r}
zip = remDr$findElement("id", "region__input--zip")
```
Here we tell it which selector method we are using ("id"), and then the selector.

Now that we have the element, we can send it the ZIP code and have it insert them:
```{r}
zip$sendKeysToElement(list("45201\n"))
```
Note that we put the text in a list. This is necessary.
<!-- zip$clickElement() -->


Now we have to click on the ENTER link.
We find the element and then click it, i.e. send a click event to it:
```{r}
enter = remDr$findElement("id", "region__link--enter")
enter$clickElement()
```

This action then brings up the `Enroll Now` option.
So again, we find that element and send a click event to it:
```{r}
enroll = remDr$findElement("xpath", "//a[. = 'Enroll Now']")
enroll$clickElement()
```

The browser then retrieves the page with the different electricity rate offers
and displays this. This is the one we want.
We can identify the elements we want within this page using 
the `findElement()` method and any of the selector methods.
However, we can also just bring the entire page back to R and use our
the methods we have learned earlier.
To get the HTML source of the document currently visible  in the browser,
we use
```{r}
txt = remDr$getPageSource()
```
This is a list that contains the HTML as a single string.
We can pass it directly to the `htmlParse()` function
and then we have a parsed HTML tree:
```{r}
library(XML)
doc = htmlParse(txt, asText = TRUE)
```

Our next task is to find the cents per kWH (kilowatt hour) values in the page
We can find the pattern to identify these by looking at the HTML source
or by extract a value we see and then going up the tree.
For this ZIP code, there is a valye of 6.09 cents. So we can find this text in the page
and get its grandparent:
```{r}
getNodeSet(doc, "//text()[contains(., '6.09')]/../..")[[1]]
```
Why the grandparent?  Lucky guess. We adjust up and down as we explore to find a distinguishing pattern.

The resulting node is 
```
<div class="offer-header">
                <div class="btn-select-mobile" data-automation="offers__button--mobile">
                  <i class="icon-checked-offer"/>
                </div>
                <div class="meta offer-months" data-automation="offers__label--month">
                  <span><b class="big-month">12</b></span>
                  <span>
                  months
                </span>
                </div>
                <div class="header offer-price" data-automation="offers__label--header-price">
                  <span class="price-symbol hidden">¢</span>
                  6.09
                  <span class="price-symbol">¢</span>
                </div>

                <div class="term-language" data-automation="offers__label--per">per kWh</div>

                <div class="term-aside" data-automation="offers__label--aside">
                  
                </div>
                <!--template bindings={}--><div class="ui flowing popup transition" style="width: 150px;">

                  <!--template bindings={}-->
                    <div class="popup-data no-left-border">
                      <div class="price-container">
                        <div class="price">
                      <span class="hidden">¢</span>
                          6.09
                          <span>¢</span>
                        </div>
                      </div>

                      <div class="popup-language">
                        per kWh
                        for 12 months
                      </div>
                    </div>

                    <div class="bottom-line"/>
                  
                </div>
                <div class="aep-btn-light btn-more-details top desktop" data-automation="offers__button--detail">
                  More
                  Details
                  <i class="icon-toggle icon-arrow-down"/>
                </div>

                <div class="line-separator">
                  <div class="inside-line"/>
                </div>

                <div class="offers-icons">
                  <!--template bindings={}--><img class="offer-icon" src="/static/enrollment/productType/desktop/DEFAULT_EL_FPAI.svg"/><!--template bindings={}--></div>
              </div> 
```

So we are looking for `<div class="offer-header">`
We can verify this by looking for the other corresponding elements
```{r}
getNodeSet(doc, "//div[@class = 'offer-header']")
```

If we just want the price rather than the entire offer, we can get this directly 
with 
```{r}
priceNodes = getNodeSet(doc, "//div[@class = 'price']/text()")
price = sapply(priceNodes, xmlValue, trim = TRUE)
```
```
 [1] ""     "6.09" ""     ""     "5.39" ""     ""     "5.41" ""    
[10] ""     "5.41" ""     ""     "5.83" ""    
```
price = price[price != ""]


If we want the details of the plans, we could click on the "More Details" link/button.
However, we suspect that the information is already in the document, just not being displayed.
Why do we suspect this? Because a) it makes sense, and b) if we click on More Details, 
the results are displayed very rapidly, indicating that there is no request back to the server
for the information.
Accordingly, let's find it in the page.

We can write the HTML text to a file and look at it in a text editor
to find the pattern. Alternatively, we can look for 'termination fee' and come back up the
tree as we did with the 6.09 text value.
We find that 
```
getNodeSet(doc, "//text()[contains(., 'termination fee')]/../../..")[[1]]
```

```
<div class="more-details-container">
                <div class="line-separator">
                  <div class="inside-line"/>
                </div>

                <div class="data-line">
                  <div class="data-title full-width" data-automation="offers__label--plan-title">Plan</div>
                  <div class="data-value full-width no-html" data-automation="offers__label--plan-value">Amazon Prime Offer</div>
                </div>

                <div class="data-line">
                  <div class="data-title full-width" data-automation="offers__label--utility-title">Utility</div>
                  <div class="data-value full-width" data-automation="offers__label--utility-value">Duke Energy</div>
                </div>

                <div class="data-line">
                  <div class="data-title full-width" data-automation="offers__label--price-title">Price</div>
                  <div class="data-value full-width">
                    <!--template bindings={}--><div class="data-value" data-automation="offers__label--price-value">
                    <span class="hidden">¢</span>
                      6.09
                      <span>¢</span>
                      <span>per kWh</span>
                      for 12 months
                    </div>
                  </div>
                </div>

                <div class="data-line">
                  <div class="data-title full-width" data-automation="offers__label--term-title">Term</div>
                  <div class="data-value full-width" data-automation="offers__label--term-value">
                    12
                    <span>
                    Months
                  </span>
                  </div>
                </div>

                <div class="data-line">
                  <div class="data-title full-width" data-automation="offers__label--fee-title">Early termination fee</div>
                  <div class="data-value sentence-text" data-automation="offers__label--fee-value">
                    $
                    99.00
                    early termination fee
                  </div>
                </div>

                <!--template bindings={}--><div class="data-line">
                  <div class="data-title full-width" data-automation="offers__label--additional-plan-title">additional plan details</div>
                  <div class="data-value full-width no-html" data-automation="offers__label--additional-plan-value">Enjoy a year of Amazon Prime on us!</div></div>

                <div class="read-more" data-automation="offers__button--read-more">
                  Read more
                </div>
                <div class="terms-conditions">
                  <a class="termsLink" data-automation="offers__button--terms" target="_blank" href="/api/media/file?key=ExiAKfOO9Cv3ttUNyJveBeiEw5CyEtmBnfRqC59C1E05cyFD18bqTCfT6yEgWHNhtR1%2FwQ15UtdfqdIEeyCjwwWJXrbQ9muUnryiJJkJtYa9Gab17QPMh3lvC3vT%2BNXGplpl1fTscoui4npwEYz3Kys8xDz93gt6qpzMfGR9HKQ%3D">
                    View full terms and conditions
                  </a>
                </div>

                <div class="line-separator last">
                  <div class="inside-line"/>
                </div>
              </div> 
```

We see that there is a <div> with a class named more-details-container and this is what we want.
We can get all 5 of these with
```{r}
details = getNodeSet(doc, "//div[@class = 'more-details-container']")
length(details)
```

Suppose we want all the details corresponding to the PLAN, UTILITY, PRICE, TERM, etc.
Each of these is within a <div> with a class data-line, and each has a title and a value
We'll write a function that takes a <div class="data-line"> node and
extracts the value and its title and return it as a named character
vector:
```
dataLine =
function(node)
{
    d = node[ names(node) == "div" ]
    val = normalizeSpace(xmlValue(d[[2]], trim = TRUE))
    title = normalizeSpace(xmlValue(d[[1]], trim = TRUE))
    structure(val, names = title)
}
```
This calls a function normalizeSpace which collapses all each block of white space to a single
space:
```
normalizeSpace =
function(x)
{
  gsub("[[:space:]]+", " ", x)
}
```

Finally, we can extract these details for each a single offer with
```
xpathSApply(details[[1]], ".//div[contains(@class, 'data-line')]", dataLine)
```

and for all offers with
```
lapply(details, function(offer) xpathSApply(offer, ".//div[contains(@class, 'data-line')]", dataLine))
```

<!-- #rD = rsDriver(browser = "phantomjs") -->
